Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-16 icse/paper.tex
Abstract

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt because it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, a developer should refactor the codebase. The thresholds and prioritization of the clones detected by current clone detection tools can be improved by considering the maintainability of the codebase after a detected clone would be refactored.

We perform an exploratory study into the data that can be gathered from comparing before- and after snapshots of an automatically refactored system. We propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems. These metrics are system size, cyclomatic complexity, duplication and number of method parameters. On the basis of these results, we decide which clones improve system design and thus should be refactored. %We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects. This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.
\end{abstract}

>>>>

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt because it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems, but failed to determine whether a duplicate fragment would improve the maintainability of the codebase when refactored.

We perform an exploratory study into the data that can be gathered from comparing before- and after snapshots of an automatically refactored system. We propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the system. On the basis of these results, we decide which clones improve system design and thus should be refactored. %We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects. %This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.

We have identified that the size of the duplication problem is the biggest influencing factor on system maintainability. We found that the majority of duplicates spanning 29 or more tokens improve maintainability when refactored. Another maintainability influencing factor is the amount of data that needs to be passed to the merged location of the duplicate.
\end{abstract}
